### 2021-04-20 conclusions.tex
other changes

As future work, we would like to further validate our approach and
improve our admittedly \emph{ad hoc} mutant distance metric.  Allowing
user feedback \cite{EndUserMistake,OnlyOracle}, or applying metric
learning methods \cite{kulis2012metric} (particularly unsupervised
learning \cite{scholkopf1998nonlinear,tipping1999probabilistic}) are
the most obvious and interesting possibilities for a better metric.
Finally, mutant prioritization should be applicable to improving
software testing, as well \cite{groce2018verified}.

>>>>

As future work, we would like to further validate our approach and
improve our admittedly \emph{ad hoc} mutant distance metric.  Allowing
user feedback \cite{EndUserMistake,OnlyOracle}, or applying metric
learning methods \cite{kulis2012metric} (particularly unsupervised
learning \cite{scholkopf1998nonlinear,tipping1999probabilistic}) are
the most obvious and interesting possibilities.
%for a better metric.
%Finally, mutant prioritization should be applicable to improving
%software testing, as well \cite{groce2018verified}.

### 2021-04-20 prioritizing.tex
other changes

In order to apply FPF ranking to examining mutants, we implemented a
simple, somewhat \emph{ad hoc} distance metric and FPF ranker in the
Universal Mutator \cite{universalmutator} tool.  Our metric $d$ is
the sum of a set of measurements.  First, it adds a similarity
ratio based on Levenshtein distance \cite{lev} for (1) the \emph{changes} (Levenshtein edits) from
the original source code elements to
the two mutants,  (2) the two original source code elements changed (in
general, lines), and (3) the actual output mutant code.  These are
weighted with multipliers of 5.0, 0.1, and 0.1, respectively; the type
of change (mutation operator, roughly) dominates this part of the
distance, because it best describes ``what the mutant did''; however,
because many mutants will have the same change (e.g., changing {\tt +}
to {\tt -}, the other ratios also often matter.
%The Python
%{\tt Levenshtein} library's similarity ratio is used, as it is based
%on true minimal string edits; it reports similarity ratios between 0.0
%and 1.0.
Our metric also incorporates a measure of the distance in the source
code between the locations of two mutants.  If the mutants are to
different files, this adds 0.5 to the distance; it also adds 0.25
times the number of source lines separating the two mutants if they
are in the same file, divided by 10, but caps the amount added at
0.25.  The full metric, therefore is:

>>>>

In order to apply FPF ranking to examining mutants, we implemented a
simple, somewhat \emph{ad hoc} distance metric and FPF ranker in the
Universal Mutator \cite{universalmutator} tool.  Our metric $d$ is
the sum of a set of measurements.  First, it adds a similarity
ratio based on Levenshtein distance \cite{lev} for (1) the \emph{changes} (Levenshtein edits) from
the original source code elements to
the two mutants,  (2) the two original source code elements changed (in
general, lines), and (3) the actual output mutant code.  These are
weighted with multipliers of 5.0, 0.1, and 0.1, respectively; the type
of change (mutation operator, roughly) dominates this part of the
distance, because it best describes ``what the mutant did''; however,
because many mutants will have the same change (e.g., changing {\tt +}
to {\tt -}, the other ratios also often matter.
%The Python
%{\tt Levenshtein} library's similarity ratio is used, as it is based
%on true minimal string edits; it reports similarity ratios between 0.0
%and 1.0.
Our metric also incorporates a measure of the distance in the source
code between the locations of two mutants.  If the mutants are to
different files, this adds 0.5; it also adds 0.25
times the number of source lines separating the two mutants if they
are in the same file, divided by 10, but caps the amount added at
0.25.  The full metric, therefore is:
